Assessing reliability of an online behavioural laterality battery: a pre-registered study (draft notebook)

### 2020-06-08 draft_notebook_writeup.Rmd
minor changes to echo and include commands so we can see tables in html version

```{r Table1,echo=FALSE,include=TRUE}
#Needs more formatting. For word output may need to use flextable. See https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
combotable%>%
  kable() %>%
  kable_styling("condensed")

@@

```{r makecontingencies,echo=FALSE,include=TRUE}
#We start by using z-scores to make a 3-way categorisation into:
#1 sig bias in typical direction; 2: NS bias 3: in atypical direction with sig bias.
#
LIs$rhyme1.cut <- cut(LIs$Day1.RDT_p.corr_LI, 
                       breaks = c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("TypLat", "Nonlat", "AtypLat"), 
                       right = FALSE)
LIs$dichotic1.cut <- cut(LIs$Day1_Dich_acc_Z, 
                       breaks = c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("TypLat", "Nonlat", "AtypLat"), 
                       right = FALSE)
LIs$chimeric1.cut <- cut(LIs$Day1_CF_acc_Z, 
                       breaks =  c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("AtypLat", "Nonlat", "TypLat"), 
                       right = FALSE)
mytabr <- table(LIs$rhyme1.cut)
mytabd <- table(LIs$dichotic1.cut)
mytabc <- table(LIs$chimeric1.cut)
mytabc<-mytabc[c(3,2,1)]
mytab2 <-rbind(mytabr,mytabd,mytabc)
row.names(mytab2)<-c('Rhyme decision','Dichotic','Chimeric Faces')
mytab2<-data.frame(mytab2)

@@

Table 2: Rhyme judgement
```{r showtabr,echo=FALSE,include=TRUE}
tabr%>%
  kable() %>%
  kable_styling("condensed")
```
Table 3: Dichotic listening
```{r showtabd,echo=FALSE,include=TRUE}
tabd%>%
  kable() %>%
  kable_styling("condensed")
```
Table 4: Chimeric faces
```{r showtabc,echo=FALSE,include=TRUE}
tabc%>%
  kable() %>%
  kable_styling("condensed")
```
It is evident that the Rhyme Judgement task has few individuals who are significantly lateralised in either direction. We will therefore not consider it further, as our analyses are only justified if the task is an indicator of cerebral lateralisation. Both Dichotic Listening and Chimeric Faces, on the other hand, are strongly lateralised.  The planned analyses, just comparing typically lateralised with atypically lateralised individuals, and extreme left vs right-handed individuals, show significant association between extreme left-handedness and atypical laterality on chi square test. For dichotic listening, chi squared = `r round(chi.d$statistic,2)`, d.f. = 1, p = `r round(chi.d$p.value,3)`; for chimeric faces, chi squared = `r round(chi.c$statistic,2)`, d.f. = 1, p = `r round(chi.c$p.value,3)`.

@@

```{r prep_dat,echo=FALSE,include=TRUE}
# now create subset of data frame for analysis
mycols <- c('Day1.RDT_RT_LI', 'Day2.RDT_RT_LI',
            'Day1_CF_acc_LI', 'Day2_CF_acc_LI',
            'Day1_DL_acc_LI', 'Day2_DL_acc_LI',
            'Day1_finger_LI', 'Day2_finger_LI',
            'handedness')
colnums<- which(colnames(LIs) %in% mycols)
M <- LIs[,colnums]
M <- M %>% 
  rename(
    "rhyme1" = Day1.RDT_RT_LI,
    "rhyme2" = Day2.RDT_RT_LI,
    "chimeric1" = Day1_CF_acc_LI,
    "chimeric2" = Day2_CF_acc_LI,
    "dichotic1" = Day1_DL_acc_LI,
    "dichotic2" = Day2_DL_acc_LI,
    "finger1" = Day1_finger_LI,
    "finger2" = Day2_finger_LI)
# subset into right and left handers
left_dat <- subset(M, handedness== "Left")
right_dat <- subset(M, handedness== "Right")
```

```{r showcorrs,echo=FALSE,include=TRUE}
#Will focus just on Day1
#Had considered showing as correlation heatmap - but values so small it wouldn't be worth doing!

@@

### Table 5: Intratask correlations for Left handers
```{r dotab5,echo=FALSE,include=TRUE}
corrL%>%
  kable() %>%
  kable_styling("condensed")
```

### Table 6: Intratask correlations for Right handers
```{r dotab6,echo=FALSE,include=TRUE}
corrR%>%
  kable() %>%
  kable_styling("condensed")
```
<!---I have run out of steam at this point. I think some of the correlations in *left-handers* might be statistically significant, though very small. But the only ones that look at all nonzero are with rhyme! Will just redo for time 2 to see if this is robust-->

@@

### Table 7: Intratask correlations time 2, for Left handers
```{r dotab7,echo=FALSE,include=TRUE}
corrL%>%
  kable() %>%
  kable_styling("condensed")
```

### Table 8: Intratask correlations time 2 ,for Right handers
```{r dotab8,echo=FALSE,include=TRUE}
corrR%>%
  kable() %>%
  kable_styling("condensed")

## SEM model 
Here we model left hander data with three prespecified covariance structures, then compare using AIC weights.

@@

```{r Roger_mod_left,echo=FALSE,include=TRUE}
model1<-"
dichotic1~~0*rhyme1
dichotic1~~0*chimeric1 
rhyme1~~0*chimeric1 
"

@@

```{r Roger_mod_right,echo=FALSE,include=TRUE}
#We now repeat this for right handers. 
fit1B <- cfa(model1, data=right_dat)
fit2B <- cfa(model2, data=right_dat)
fit3B <- cfa(model3, data=right_dat)

>>>>

```{r Table1,echo=FALSE}
#Needs more formatting. For word output may need to use flextable. See https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
combotable%>%
  kable() %>%
  kable_styling("condensed")

@@

```{r makecontingencies,echo=FALSE}
#We start by using z-scores to make a 3-way categorisation into:
#1 sig bias in typical direction; 2: NS bias 3: in atypical direction with sig bias.
#
LIs$rhyme1.cut <- cut(LIs$Day1.RDT_p.corr_LI, 
                       breaks = c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("TypLat", "Nonlat", "AtypLat"), 
                       right = FALSE)
LIs$dichotic1.cut <- cut(LIs$Day1_Dich_acc_Z, 
                       breaks = c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("TypLat", "Nonlat", "AtypLat"), 
                       right = FALSE)
LIs$chimeric1.cut <- cut(LIs$Day1_CF_acc_Z, 
                       breaks =  c(-Inf, -1.96, 1.96, Inf), 
                       labels = c("AtypLat", "Nonlat", "TypLat"), 
                       right = FALSE)
mytabr <- table(LIs$rhyme1.cut)
mytabd <- table(LIs$dichotic1.cut)
mytabc <- table(LIs$chimeric1.cut)
mytabc<-mytabc[c(3,2,1)]
mytab2 <-rbind(mytabr,mytabd,mytabc)
row.names(mytab2)<-c('Rhyme decision','Dichotic','Chimeric Faces')
mytab2<-data.frame(mytab2)

@@

Table 2: Rhyme judgement
```{r showtabr,echo=FALSE}
tabr%>%
  kable() %>%
  kable_styling("condensed")
```
Table 3: Dichotic listening
```{r showtabd}
tabd%>%
  kable() %>%
  kable_styling("condensed")

Table 4: Chimeric faces
```{r showtabc,echo=FALSE}
tabc%>%
  kable() %>%
  kable_styling("condensed")

```
It is evident that the Rhyme Judgement task has few individuals who are significantly lateralised in either direction. We will therefore not consider it further, as our analyses are only justified if the task is an indicator of cerebral lateralisation. Both Dichotic Listening and Chimeric Faces, on the other hand, are strongly lateralised.  The planned analyses, just comparing typically lateralised with atypically lateralised individuals, and extreme left vs right-handed individuals, show significant association between extreme left-handedness and atypical laterality on chi square test. For dichotic listening, chi squared = `r round(chi.d$statistic,2)`, d.f. = 1, p = `r round(chi.d$p.value,3)`; for chimeric faces, chi squared = `r round(chi.c$statistic,2)`, d.f. = 1, p = `r round(chi.c$p.value,3)`.

@@

```{r prep_dat,echo=FALSE}
# now create subset of data frame for analysis
mycols <- c('Day1.RDT_RT_LI', 'Day2.RDT_RT_LI',
            'Day1_CF_acc_LI', 'Day2_CF_acc_LI',
            'Day1_DL_acc_LI', 'Day2_DL_acc_LI',
            'Day1_finger_LI', 'Day2_finger_LI',
            'handedness')
colnums<- which(colnames(LIs) %in% mycols)
M <- LIs[,colnums]
M <- M %>% 
  rename(
    "rhyme1" = Day1.RDT_RT_LI,
    "rhyme2" = Day2.RDT_RT_LI,
    "chimeric1" = Day1_CF_acc_LI,
    "chimeric2" = Day2_CF_acc_LI,
    "dichotic1" = Day1_DL_acc_LI,
    "dichotic2" = Day2_DL_acc_LI,
    "finger1" = Day1_finger_LI,
    "finger2" = Day2_finger_LI)
# subset into right and left handers
left_dat <- subset(M, handedness== "Left")
right_dat <- subset(M, handedness== "Right")
```

```{r showcorrs,echo=FALSE}
#Will focus just on Day1
#Had considered showing as correlation heatmap - but values so small it wouldn't be worth doing!

@@

### Table 5: Intratask correlations for Left handers
```{r dotab5,echo=FALSE}
corrL%>%
  kable() %>%
  kable_styling("condensed")
```

### Table 6: Intratask correlations for Right handers
```{r dotab6,echo=FALSE}
corrR%>%
  kable() %>%
  kable_styling("condensed")
```
<!---I have run out of steam at this point. I think some of the correlations in *left-handers* might be statistically significant, though very small. But the only ones that look at all nonzero are with rhyme! Will just redo for time 2 to see if this is robust-->

@@

### Table 7: Intratask correlations time 2, for Left handers
```{r dotab7,echo=FALSE}
corrL2%>%
  kable() %>%
  kable_styling("condensed")
```

### Table 8: Intratask correlations time 2 ,for Right handers
```{r dotab8,echo=FALSE}
corrR2%>%
  kable() %>%
  kable_styling("condensed")
```

## SEM model

Here we model left hander data with three prespecified covariance structures, then compare using AIC weights.

@@

```{r Roger_mod_left,echo=FALSE}
model1<-"
dichotic1~~0*rhyme1
dichotic1~~0*chimeric1 
rhyme1~~0*chimeric1 
"

@@

```{r Roger_mod_right,echo=FALSE}
#We now repeat this for right handers. 
fit1B <- cfa(model1, data=right_dat)
fit2B <- cfa(model2, data=right_dat)
fit3B <- cfa(model3, data=right_dat)
